---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Bitter:ital@0;1&display=swap');

body {
  font-family: "Bitter", serif;
  max-width: fit-content;
  margin: 16px auto;
}

h1, h2, h3 {
  text-align: center;
}
```

## Weather observations in Auckland

This report summarises data from personal observations of the weather in Auckland.\
The observations include time of day, if it was raining, how cloudy the sky was, and an estimated temperature (Celsius). 

```{r}
library(tidyverse)

logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQdi_PTeRYXy86fjntETypel6XaYZlslTKppRUPK-SFfYFigQZWfIsr7YvnVt_MsohWxe13p5Zi0Qkh/pub?gid=427691419&single=true&output=csv")

latest_data = logged_data %>%
  rename(timestamp = 1,
         time_of_day = 2,
         was_raining = 3,
         cloudiness = 4,
         estimated_temp = 5)
```

```{r}
total_entries <- length(latest_data$timestamp)

max_temp <- max(latest_data$estimated_temp)
min_temp <- min(latest_data$estimated_temp)

rainy_count <- sum(latest_data$was_raining == "Yes")
rain_pct <- round((rainy_count / total_entries) * 100, 1)
```

## The data
There have been a total of `r total_entries` observations so far.\
Out of these observations, it was raining `r rain_pct`% of the time, with temperature estimates ranging from `r min_temp`°C to `r max_temp`°C.

### When were the observations taken?

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = time_of_day), fill = "lightgreen") +
  labs(
    title = "Observations by Time of Day",
    x     = "Time of Day",
    y     = "Amount"
  )
```

### How cloudy was it when it rained?

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = cloudiness, fill = was_raining)) +
  labs(
    title = "How cloudy was it when it rained?",
    x     = "Cloudiness",
    y     = "Amount",
    fill  = "Was Raining?"
  )
```
